Ecuador plant species GBIF cleaning

### 2022-10-17 code/L1/L1_Ecuador_plants_GBIF.Rmd
Add checks in data validation Add duplicate specimen code

# Load required packages
```{r}
install.packages("remotes")
library("remotes")
install_github("LimaRAF/plantR")
library("plantR")
```

@@

# Standardize data
```{r}
# Field names
occs <- formatDwc(gbif_data = gbif_data, drop = TRUE)
dim(occs)
```

@@

# Data validation
```{r}
# Locality information
occs <- validateLoc(occs)
# Geographical coordinates
occs <- validateCoord(occs)
# Species taxonomy and identification
occs <- validateTax(occs)
# Duplicate specimens
occs <- validateDup(occs)
```

# Data Summary and Export
```{r}
summ <- summaryData(occs)
flags <- summaryFlags(occs)
```

```{r}
Ecuador_GBIF_path <- file.path(output_path,"Ecuador_GBIF_occurences_plantR.csv") 
write.csv(d, file = Ecuador_GBIF_path)
```

>>>>

# Load required packages
```{r}
#remotes::install_github("LimaRAF/plantR")
library("plantR")
```

@@

# Standardize data
```{r}
# Field names
occs <- formatDwc(gbif_data = gbif_data)
dim(occs)
```

@@

# Data validation
```{r}
# Locality information
occs <- validateLoc(occs)
unique(occs$loc.check)
```

```{r}
# Geographical coordinates
occs <- validateCoord(occs)
unique(occs$geo.check)
table(occs$cult.check)
```

```{r}
# Species taxonomy and identification
occs <- validateTax(occs)
table(occs$tax.check)/dim(occs)[1]
```

```{r}
# Duplicate specimens
dups <- prepDup(occs, 
                comb.fields =   list(c("family","col.last.name","col.number","col.loc"),
     c("family","col.last.name","col.number","col.year")))
dups <- getDup(dups)
head(dups[order(dups$dup.ID),],6)
table(dups$dup.prop)
occs <- cbind.data.frame(occs, 
                         dups[,c("dup.ID", "dup.numb", "dup.prop")],
                         stringsAsFactors = FALSE)
occs <- mergeDup(occs)
table(occs$tax.check, occs$tax.check1)
table(occs$geo.check, occs$geo.check1)
table(occs$loc.check, occs$loc.check1)
occs <- validateDup(occs)
```

# Data Summary and Export
```{r}
summ <- summaryData(occs)
flags <- summaryFlags(occs)
spp.check <- checkList(occs)
```

```{r}
saveData(occs, by = "family")
Ecuador_GBIF_path <- file.path(output_path,"Ecuador_GBIF_occurences_plantR.csv") 
write.csv(d, file = Ecuador_GBIF_path)
```
